Constructing a universe for the setoid model

### 2020-07-08 paper.tex
Minor change to the conclusions

As further work, we would like to investigate a construction of the setoid
universe that does not require a strong transport rule for the proof-irrelevant
identity type. Not only to avoid unnecessary extensions to the metatheory, but
also because we don't yet know whether $\mlttp$ extended with this rule is
normalizing.
%
Indeed, previous work in this respect \cite{abel2019failure} seems to suggest
that this rule is a non-trivial addition to the metatheory.

>>>>

Our inductive definition of the setoid universe relies on a metatheory with a
strong transport rule. As future work, we would like to prove normalization for
this metatheory, since we don't yet know if this property holds in the presence
of such rule, and previous work in this respect \cite{abel2019failure} seems to
suggest that is represents a non-trivial addition.
%
An alternative path worth investigating is to find a construction of the
universe that does not rely on strong transport. Note that this issue only
involves the inductive definition, as the inductive-recursive and
inductive-inductive versions do not need strong transport.
